Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex
Beginnings of joining "Components of Ceph..." with "Malacology Implementation"

\section{Components of Ceph Suitable for Reusability}\label{re-usable-components-in-ceph}

\label{background}

Ceph is a production-quality distributed storage system and in this section we
touch on some of the subsystems it uses to provide a general-purpose
storage system. In the next section, we describe how Malacology exposes these
subsystems in order to make them reusable and enable the creation of new services on top of them.

@@

In order to reduce load on the monitoring service, Ceph OSDs use a gossip
protocol to efficiently propogate changes to cluster maps throughout the
system, and automonmously initiate recovery mechansims when failures are
discovered.

@@

@@

The distributed metadata service in Ceph provides clients with a POSIX file
system abstraction. Distributed file systems are complex, but fundamentally
provide durable hierarhical indexing and distributed locking service.  The
locking service implements a capabilities that express what data and metadata
clients are allowed to access as well as what they may cache locally.  While
designed for a fixed file abstraction, indexing, locking, and caching are all
common services that are useful to large sets of applications.

>>>>

\section{Malacology}
\label{sec:malacology}

Malacology is both a prototype for a programmable storage system and a design approach to evolve storage systems efficiently and without
jeopardizing years of code-hardening and performance optimization
efforts. The guiding principle is to re-use existing services and extend them so that these services can be \emph{programmed}. We accomplish programmability of a service by exporting bindings (or ``hooks'') for an interpreted programming language so that programming can occur without having to restart the storage system (see also below,~\S\ref{sec:durability}).

We will now discuss the subsystems Ceph uses to provide a general-purpose
storage system and how Malacology makes them programmable.

In order to reduce load on the monitoring service, Ceph OSDs use a gossip
protocol to efficiently propagate changes to cluster maps throughout the
system, and automonmously initiate recovery mechansims when failures are
discovered.

\paragraph*{Malacology:} The implementation of Ceph's object abstraction, although powerful, has some 
drawbacks.
Supporting only C/C++ for object interface developers, Ceph requires
distribution of compiled binaries for the correct architecture, adding a
large barrier of entry for developers and system administrators. Second,
having no way to dynamically unload modules, any changes require a full
restart of an OSD which may have serious performance impacts due to a loss
of cached data. And finally, the security limitations of the framework
limit the use of object classes to all but those with administrative level
access and technique expertise.

@@

\paragraph*{Malacology:} Map modification for propogation of state. We allow applications to augment
these data structures with application-specific metdata. In order to keep the
size of these data structures small application state may be stored elsewhere
and the references stored within the data structure.

@@

\paragraph*{Malacology:}

@@

The distributed metadata service in Ceph provides clients with a POSIX file
system abstraction. Distributed file systems are complex, but fundamentally
provide durable hierarchical indexing and distributed locking service.  The
locking service implements a capabilities that express what data and metadata
clients are allowed to access as well as what they may cache locally.  While
designed for a fixed file abstraction, indexing, locking, and caching are all
common services that are useful to large sets of applications.
